Death By Dropdown?

### 2025-04-04 conference-materials/2025_shiny-conf/slides.qmd
Added QR codes to final slide
Cleans up slides 5 & 6 and the thank you slide
- Adds new images for slides
- Updates slide formatting for better readability and incorporates a callout to highlight BID framework's key differentiator
- Renames files for consistency and updates themes for slides.

---
title: "Death By Dropdown?"
subtitle: "A Developer's Guide To Building Dashboards That Won't Fry Your Client's Brain"
author: "Milena Eickhoff & Jeremy Winget, PhD"
format: 
  revealjs:
    theme: simple
    slide-number: true
    footer: "ShinyConf 2025 | The BID Framework"
    incremental: true
    transition: slide
    background-transition: fade
    highlight-style: github
    code-block-background: true
---

@@

:::: {.columns .absolute top="58%"}

::: {.column width="27%"}
1. **Notice** the Problem
:::

::: {.column width="46%"}
2. **Interpret** the User's Need
3. **Structure** the Dashboard
4. **Anticipate** User Behavior
:::

::: {.column width="27%"}
5. **Validate** & Empower the User
:::

@@

- "The 5 stages form an easy workflow: Notice → Interpret → Structure → Anticipate → Validate"
  * Click through each
- "Each stage translates psychological principles into practical developer actions"
- "This isn't just theory - it's a step-by-step process you can implement today"
- "These stages are iterative - you'll often revisit earlier stages as you discover new insights"
:::

@@

@@

- "BID integrates existing best practices from multiple disciplines"..."We're truly standing on the shoulders of giants here"
- Key differentiator: "But what makes BID unique is its process-oriented framework vs. a typical checklist approach"
- "The goal is helping users gain clearer insights while giving developers a tool to use in their workflows"
- "Even though there's a lot of theory, you don't need a psychology degree to apply these principles effectively"
- "To demonstrate...let's take a closer look at how we connected these stages to SoundPulse's dashboard."
:::

@@

## Thank You! {.center background-color="#4682b4"}

::: {.r-fit-text}
Questions?
:::

Milena Eickhoff & Jeremy Winget, PhD

>>>>

---
title: "Death By Dropdown?"
subtitle: "A Developer's Guide To Building Dashboards That Won't Fry Your Client's Brain"
author: "Milena Eickhoff & Jeremy Winget, PhD"
format: 
  revealjs:
    theme: simple
    slide-number: false
    footer: "ShinyConf 2025 | Death By Dropdown?"
    incremental: true
    transition: slide
    background-transition: fade
    highlight-style: github
    code-block-background: true
---

@@

:::: {.columns .absolute top="65%" left="4%" .r-fit-text}

::: {.column width="38%"}
1. <span style="color:#1c6d7d">**Notice**</span> the Problem
:::

::: {.column width="46%"}
2. <span style="color:#35a4ae">**Interpret**</span> the User's Need
3. <span style="color:#ff9000">**Structure**</span> the Dashboard
4. <span style="color:#ffca90">**Anticipate**</span> User Behavior
:::

::: {.column width="16%"}
5. <span style="color:#98d3ca">**Validate**</span> & Empower the User
:::

@@

- "The 5 stages form an easy workflow: Notice → Interpret → Structure → Anticipate → Validate"
  * Click through each
- "Each stage translates psychological principles into practical developer actions"
- "This isn't just theory - it's a step-by-step process you can implement today"
- "These stages are iterative - you'll often revisit earlier stages as you discover new insights"
  * Any order
:::

@@

::: {.callout-note .mt-3}
**Key Differentiator**: Process-oriented framework vs. typical checklist approach
:::

@@

- "BID integrates existing best practices from multiple disciplines"..."We're truly standing on the shoulders of giants here"
  * Click through example fields...UX, data storytelling, psych science, data/visual communication
- Key differentiator: "But what makes BID unique is its process-oriented framework vs. a typical checklist approach"
- "The goal is helping users gain clearer insights while giving developers a tool to use in their workflows"
- "Even though there's a lot of theory, you don't need a psychology degree to apply these principles effectively"
- "To demonstrate...let's take a closer look at how we connected these stages to SoundPulse's dashboard."
:::

@@

## {data-background-image="img/thank-you.png" data-background-size="100% 100%"}

<!-- TODO: replace background image with css and brand elements in img -->

<br>
<br>

:::: {.columns}
::: {.column width="55%" .r-fit-text}
### Milena Eickhoff {style="color: white;"}
![](img/headshot-eickhoff.jpg){width="80px" height="80px" style="border-radius: 50%;"}
![](img/qr-linkedin-eickhoff.svg){width="80px" height="80px"}

### Jeremy Winget, PhD {style="color: white;"}
![](img/headshot-winget.jpg){width="80px" height="80px" style="border-radius: 50%;"}
![](img/qr-linkedin-winget.svg){width="80px" height="80px"}

![](img/lets-connect.png){width="50%"}
:::
::::
